noam_data_exploration_v1

### 2024-08-20 noam_data_exploration_v3.Rmd
added log richness as a factor for gls modeling but hit an error - will look into tomorrow.

# FRAMING: What is the general trend in algal alpha diversity over the course of the time series? Increasing, decreasing, neutral?

columns <- c("location", "Intercept", "Slope", "Phi") # names of columns for dataframe
gls_coefficients <- # new dataframe name
  data.frame(matrix(nrow = length(unique(alpha_diversity_quad$location)), # 1200 quadrats = 1200 different time series
                    ncol = length(columns)) # specified to make sure number of columns doesn't exceed what was specified
             )
colnames(gls_coefficients) <- columns # change column names to what was specified
gls_coefficients$location <- levels(alpha_diversity_quad$location) # populate location column with each quad/time series

>>>>

# FRAMING: What is the general trend in algal alpha diversity over the course of the time series? Increasing, decreasing, neutral?
alpha_diversity_quad$logRich <- log(alpha_diversity_quad$richness + 1)
columns <- c("location", "Intercept", "Slope", "Phi") # names of columns for dataframe
gls_coefficients <- # new dataframe name
  data.frame(matrix(nrow = length(unique(alpha_diversity_quad$location)), # 1200 quadrats = 1200 different time series
                    ncol = length(columns)) # specified to make sure number of columns doesn't exceed what was specified
             )
colnames(gls_coefficients) <- columns # change column names to what was specified
gls_coefficients$location <- levels(alpha_diversity_quad$location) # populate location column with each quad/time series
